Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between Sex Determination Systems

### 2017-01-31 LaTeX/Turnover.tex
paragraph added to discussion, some mentions of drive added to intro/abstract

Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female. 
Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios). 
Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
The mutations we consider here, neo-sex-determining alleles, break this assumption. 
For example, the success of neo-Y mutations depends only on the number of alleles contributed by males (equation \ref{eq:charpoly_neoY} and Table \ref{tab:haplotype_growth}). 
Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex. 
Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence that Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover}).

>>>>

Linkage between a locus that experiences haploid selection and a sex-determining region causes zygotic sex ratios to become biased \textcolor{red}{(REFERENCES)}, which we might then expect to exert sex ratio selection upon new modifiers.
Fisherian sex ratio selection follows from the fact that, for an autosomal locus, half of the genetic material is inherited from a male, and half from a female. 
Thus, if the population sex ratio is biased towards females, the average per-individual contribution of genetic material to the next generation from males is greater than the contribution from females (and vice versa for male-biased sex ratios). 
Therefore, a mutant that increases investment in males will spread via the higher per-individual contributions made by males. 
That is, under Fisherian sex ratio selection, the success of a mutant relative to the non-mutant depends, in equal parts, on the contributions made by males and females to the next generation. 
An implicit assumption of Fisherian sex ratio selection is that the mutant allele is autosomal and has the same inheritance pattern as the non-mutant allele. 
The mutations we consider here, neo-sex-determining alleles, break this assumption. 
For example, the success of neo-Y mutations depends only on the number of alleles contributed by males (equation \ref{eq:charpoly_neoY} and Table \ref{tab:haplotype_growth}). 
Even mutants that are equally likely to be found in males or females, such as an environmental sex determination mutation (equation \ref{eq:lambda_ESD}), are not strictly autosomal if they determine sex. 
Thus, despite the fact that sex ratio biases caused by haploid competition or meiotic drive have been shown to exert selection on various autosomal modifiers \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va}, we do not find evidence of Fisherian sex ratio selection acting upon neo-sex-determination systems (e.g., see Figure \ref{fig:Combination_Turnover}).
